Missing data: Current practice in football research and recommendations for reporting missingness

### 2020-09-03 paper/paper.Rmd
change wording in the intro

It is imperative that missing data, including lack thereof, are reported. However, outside of 
sports science, there is evidence that researchers seldom consider missing data [@Schafer2002]. 
While there has been significant interest in modelling missing
data [@refs], the exploration and reporting of missings have received
less attention [@Schafer2002]. This article aimed to: (1) estimate the proportion
of articles that report missing data in football research; (2) highlight
several improvable missing data practices; and (3) provide recommendations for
exploring and reporting missingness.

>>>>

It is imperative that missing data, or lack thereof, are reported. However, there is 
evidence that outside of sports science, researchers seldom consider missing data [@Schafer2002]. 
While there has been significant interest in modelling missing
data [@refs], the exploration and reporting of missings have received
less attention [@Schafer2002]. This article aimed to: (1) estimate the proportion
of articles that report missing data in football research; (2) highlight
several improvable missing data practices; and (3) provide recommendations for
exploring and reporting missingness.
